Privacy and Security Benefits of Jailbreaking iOS

### 2013-12-09 final_project/paper.tex
changed the document class to article. added hyperref for \cite() linked to the reference in bibliogrpahy
reorganized sections

\documentclass[12pt, titlepage, oneside]{amsart}
\usepackage{amsaddr}
\usepackage{setspace}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}

\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Privacy and Security Benefits of Jailbreaking iOS}
\author{Stefan Dimitrov}
\address{sdimit01@tufts.edu}
%\author{Mentor}
\author{Ming Chow}
\address{Mentor}

\author{\today}

@@

Considering these important uses of jailbreaking, in this paper I present third-party research that benefits from jailbreaking in evaluating the state of security and privacy on iOS, and showcase useful tools that can improve the security and privacy of jailbroken iOS users.
\section{Action Items}

\subsection{Threats on the App Store}

@@

\subsubsection{Sneaking malicious code into the AppStore}
Since the approval process does not require that developers submit their source code for a review, it is quite possible to use code obfuscation techniques in order to evade any static or dynamic code analysis tools Apple might be using to uncover threats.

@@

\cite{attacks}, 
\subsubsection{Threats to Privacy on the AppStore}
Even though Apple tests the applications submitted to the App Store for malicious behavior and security risks, it is even harder to check if apps \emph{misuse} user information. While techniques such as dynamic \cite{dynamic} and static \cite{pios} analysis targeted at capturing data flows within the application have been developed, several controversial cases of user data misuse and user profiling have gained attention\footnote{http://mclov.in/2012/02/08/path-uploads-your-entire-address-book-to-their-servers.html}. The problem of course is somewhat intractable, because trusting data to a third party comes with no guarantees about how the data will be used.

@@

\subsection{Jailbreaking for better privacy and security}

>>>>

\documentclass[12pt, titlepage, oneside]{article}
%\usepackage{amsaddr}
\usepackage{setspace}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{epstopdf}

\newcommand{\tab}{\hspace*{2em}}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Privacy and Security Benefits of Jailbreaking iOS}
%\author{Stefan Dimitrov}

\author{
  Stefan Dimitrov\\
  \texttt{sdimit01@tufts.edu}
  %\and
  \\\\
  Ming Chow\\
  \emph{Mentor}
}

%\address{sdimit01@tufts.edu}
%\author{Mentor}
%\author{Ming Chow}
%\address{Mentor}

%\author{\today}

@@

Considering these important uses of jailbreaking, in this paper I present third-party research that benefits from jailbreaking in evaluating the state of security and privacy on iOS, and showcase useful tools that can improve the security and privacy of jailbroken iOS users.

\section{Threats on the App Store}

@@

\subsection{Sneaking malicious code into the AppStore}
Since the approval process does not require that developers submit their source code for a review, it is quite possible to use code obfuscation techniques in order to evade any static or dynamic code analysis tools Apple might be using to uncover threats.

@@

\cite{attacks}, 
\subsection{Threats to Privacy on the AppStore}
Even though Apple tests the applications submitted to the App Store for malicious behavior and security risks, it is even harder to check if apps \emph{misuse} user information. While techniques such as dynamic \cite{dynamic} and static \cite{pios} analysis targeted at capturing data flows within the application have been developed, several controversial cases of user data misuse and user profiling have gained attention\footnote{http://mclov.in/2012/02/08/path-uploads-your-entire-address-book-to-their-servers.html}. The problem of course is somewhat intractable, because trusting data to a third party comes with no guarantees about how the data will be used.

@@

\section{Action Items}
\subsection{Jailbreaking for better privacy and security}
